### 2019-04-15 manuscript.tex
Update manuscript.tex

\documentclass[12pt,]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{url,hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

>>>>

\documentclass[12pt,]{article}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{adjustbox}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage{longtable}
\usepackage{url,hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\FloatBarrier

\section{Figures}

\subsection{Daughter Plan}
\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/daughterPlan_effects_plot.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/daughterPlan_isoplots.Rout.pdf}
\end{figure}
\end{center}

\newpage

\subsection{FGC Persistence}
\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/fgcPersist_effects_plot.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/fgcPersist_isoplots.Rout.pdf}
\end{figure}
\end{center}

\newpage

\subsection{Hybrid Model}
\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/hybrid_effects_plot.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/hybrid_isoplots.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7,page=2]{./git_push/hybrid_isoplots.Rout.pdf}
\end{figure}
\end{center}

\FloatBarrier
